\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Tweak figure and caption

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Comparison to other pairs that show abundance differences.
    %TODO
    Abundance differences of the \bizarreone-\sunanalog\ pair ranked by the
    condensation temperature of elements for solar composition
    gas\cite{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1\cite{Mack:2014aa} ($\feh\approx0$),
    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$),
    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Comparison to other pairs that show abundance differences.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas\cite{2003ApJ...591.1220L} on the $x$-axis, same as \figname~\ref{fig:deltaxh_tcrank}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1\cite{Mack:2014aa} ($\feh\approx0$),
    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$),
    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by vertical lines and their symbols.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}
